### 2022-04-28 manuscript/manuscript.Rmd
fixed bug arising from using everything with across

  # Recode NAs to FALSE
  mutate(across(
    everything()
    , ~replace_na(., FALSE) )) %>% 
  select(esi_field, starts_with("has_")) %>% 
  group_by(esi_field) %>%
  summarise(across(starts_with("has_"), list(n = sum, N = ~n()), .names = "{col}__{fn}")) %>%
  adorn_totals(name = 'OVERALL') %>%
  pivot_longer(cols = !esi_field, names_to = c('variable', '.value'), names_sep = '__', names_prefix = 'has_') %>%
  mutate(prop = n/N, percent = prop*100) %>%
  mutate(esi_abbr = case_when( # create abbreviated field labels to use in figures
    esi_field == "OVERALL" ~ "OVERALL",
    esi_field == "AGRICULTURAL SCIENCES" ~ "AGRI",
    esi_field == "BIOLOGY & BIOCHEMISTRY" ~ "BIO",       
    esi_field == "CHEMISTRY" ~ "CHEM" ,                   
    esi_field == "CLINICAL MEDICINE" ~ "MED",           
    esi_field == "COMPUTER SCIENCE" ~ "COM",             
    esi_field == "ECONOMICS & BUSINESS" ~ "ECON",         
    esi_field == "ENGINEERING" ~ "ENG",                  
    esi_field == "ENVIRONMENT_ECOLOGY" ~ "ECO",         
    esi_field == "GEOSCIENCES" ~ "GEO",                  
    esi_field == "IMMUNOLOGY" ~ "IMM",                   
    esi_field == "MATERIALS SCIENCE" ~ "MATSCI",            
    esi_field == "MATHEMATICS" ~ "MATH",                
    esi_field == "MICROBIOLOGY" ~ "MICBIO",                 
    esi_field == "MOLECULAR BIOLOGY & GENETICS" ~ "MOLBIO", 
    esi_field == "Multidisciplinary" ~ "MULTI",            
    esi_field == "NEUROSCIENCE & BEHAVIOR" ~ "NEURO",     
    esi_field == "PHARMACOLOGY & TOXICOLOGY" ~ "PHARM",    
    esi_field == "PHYSICS" ~ "PHYS",                     
    esi_field == "PLANT & ANIMAL SCIENCE" ~ "PLANT",       
    esi_field == "PSYCHIATRY_PSYCHOLOGY" ~ "PSY",       
    esi_field == "SOCIAL SCIENCES, GENERAL" ~ "SOC",     
    esi_field == "SPACE SCIENCE" ~ "SPACE"          
  )) %>%
  mutate(esi_field_with_abbr = paste0(esi_field,' (', esi_abbr,')')) %>%
  mutate(var_display = case_when( # create display versions of topic names
    variable == "guidance" ~ "Provides any statistical guidance",
    variable == "internal_guidance" ~ "Provides journal-specific statistical guidance",
    variable == "internal_guidance_section" ~ "Dedicated statistical guidance section",
    variable == "external_guidance" ~ "External statistical guidance",
    variable == "p_value" ~ "p values",
    variable == "significance" ~ "statistical significance",
    variable == "null_hypo" ~ "null hypotheses",
    variable == "sample_size" ~ "sample size",
    variable == "conf_int" ~ "confidence intervals",
    variable == "effect_size" ~ "effect sizes",
    variable == "multi_compare" ~ "multiple comparisons",
    variable == "subgroup" ~ "subgroup analyses",
    variable == "baseline_covar" ~ "baseline covariates",
    variable == "non_param" ~ "non-parametric tests",
    variable == "sensitivity" ~ "sensitivity analyses",
    variable == "model_assume" ~ "model assumptions",
    variable == "exclusion" ~ "data exclusions",
    variable == "outliers" ~ "outliers",
    variable == "missing" ~ "missing data",
    variable == "one_sided" ~ "one-tailed tests",
    variable == "bayes" ~ "Bayesian statistics",
    variable == "secondary" ~ "secondary outcomes",
    variable == "prespecify" ~ "prespecify analyses",
    variable == "cat_continuous" ~ "CCV",
    variable == "publisher_guidance" ~ "Shares publisher guidance"
  ))

@@

```{r how_much_guidance}
n_topics <- d_all %>% filter(has_guidance == T, has_internal_guidance == T) %>%
  mutate(across(everything(), ~replace_na(., FALSE) )) %>% # Recode NAs to FALSE
  select(journal, starts_with("has_"), -c(has_guidance, has_internal_guidance, has_internal_guidance_section, has_external_guidance, has_publisher_guidance)) %>%
  pivot_longer(cols = !journal, names_to = 'topic', values_to = 'value') %>%
  group_by(journal) %>%
  summarise(topics_mentioned = sum(value))
```

@@

>>>>

  # Recode NAs to FALSE
  mutate(across(
    starts_with('has_'), ~replace_na(., FALSE) )) %>% 
  select(esi_field, starts_with("has_")) %>% 
  group_by(esi_field) %>%
  summarise(across(starts_with("has_"), list(n = sum, N = ~n()), .names = "{col}__{fn}")) %>%
  adorn_totals(name = 'OVERALL') %>%
  pivot_longer(cols = !esi_field, names_to = c('variable', '.value'), names_sep = '__', names_prefix = 'has_') %>%
  mutate(prop = n/N, percent = prop*100) %>%
  mutate(esi_abbr = case_when( # create abbreviated field labels to use in figures
    esi_field == "OVERALL" ~ "OVERALL",
    esi_field == "AGRICULTURAL SCIENCES" ~ "AGRI",
    esi_field == "BIOLOGY & BIOCHEMISTRY" ~ "BIO",       
    esi_field == "CHEMISTRY" ~ "CHEM" ,                   
    esi_field == "CLINICAL MEDICINE" ~ "MED",           
    esi_field == "COMPUTER SCIENCE" ~ "COM",             
    esi_field == "ECONOMICS & BUSINESS" ~ "ECON",         
    esi_field == "ENGINEERING" ~ "ENG",                  
    esi_field == "ENVIRONMENT_ECOLOGY" ~ "ECO",         
    esi_field == "GEOSCIENCES" ~ "GEO",                  
    esi_field == "IMMUNOLOGY" ~ "IMM",                   
    esi_field == "MATERIALS SCIENCE" ~ "MATSCI",            
    esi_field == "MATHEMATICS" ~ "MATH",                
    esi_field == "MICROBIOLOGY" ~ "MICBIO",                 
    esi_field == "MOLECULAR BIOLOGY & GENETICS" ~ "MOLBIO", 
    esi_field == "Multidisciplinary" ~ "MULTI",            
    esi_field == "NEUROSCIENCE & BEHAVIOR" ~ "NEURO",     
    esi_field == "PHARMACOLOGY & TOXICOLOGY" ~ "PHARM",    
    esi_field == "PHYSICS" ~ "PHYS",                     
    esi_field == "PLANT & ANIMAL SCIENCE" ~ "PLANT",       
    esi_field == "PSYCHIATRY_PSYCHOLOGY" ~ "PSY",       
    esi_field == "SOCIAL SCIENCES, GENERAL" ~ "SOC",     
    esi_field == "SPACE SCIENCE" ~ "SPACE"          
  )) %>%
  mutate(esi_field_with_abbr = paste0(esi_field,' (', esi_abbr,')')) %>%
  mutate(var_display = case_when( # create display versions of topic names
    variable == "guidance" ~ "Provides any statistical guidance",
    variable == "internal_guidance" ~ "Provides journal-specific statistical guidance",
    variable == "internal_guidance_section" ~ "Dedicated statistical guidance section",
    variable == "external_guidance" ~ "External statistical guidance",
    variable == "p_value" ~ "p values",
    variable == "significance" ~ "statistical significance",
    variable == "null_hypo" ~ "null hypotheses",
    variable == "sample_size" ~ "sample size",
    variable == "conf_int" ~ "confidence intervals",
    variable == "effect_size" ~ "effect sizes",
    variable == "multi_compare" ~ "multiple comparisons",
    variable == "subgroup" ~ "subgroup analyses",
    variable == "baseline_covar" ~ "baseline covariates",
    variable == "non_param" ~ "non-parametric tests",
    variable == "sensitivity" ~ "sensitivity analyses",
    variable == "model_assume" ~ "model assumptions",
    variable == "exclusion" ~ "data exclusions",
    variable == "outliers" ~ "outliers",
    variable == "missing" ~ "missing data",
    variable == "one_sided" ~ "one-tailed tests",
    variable == "bayes" ~ "Bayesian statistics",
    variable == "secondary" ~ "secondary outcomes",
    variable == "prespecify" ~ "prespecify analyses",
    variable == "cat_continuous" ~ "CCV",
    variable == "publisher_guidance" ~ "Shares publisher guidance"
  ))

@@

```{r how_much_guidance}
n_topics <- d_all %>% filter(has_guidance == T, has_internal_guidance == T) %>%
  mutate(across(starts_with('has_'), ~replace_na(., FALSE) )) %>% # Recode NAs to FALSE
  select(journal, starts_with("has_"), -c(has_guidance, has_internal_guidance, has_internal_guidance_section, has_external_guidance, has_publisher_guidance)) %>%
  pivot_longer(cols = !journal, names_to = 'topic', values_to = 'value') %>%
  group_by(journal) %>%
  summarise(topics_mentioned = sum(value))
```

@@

# (APPENDIX) Appendix {-}

```{r child = "supplementary_information.Rmd"}
```

### 2022-04-28 manuscript/supplementary_information.Rmd
fixed bug arising from using everything with across

# list of journals in order of most topics mentioned
journals_topics_mentioned_ordered <- d_internal_guidance %>%
  # Recode NAs to FALSE
  mutate(across(
    everything()
    , ~replace_na(., FALSE) )) %>% 
  mutate(journal = toupper(journal)) %>%
  select(journal, starts_with("has_"), -c(has_guidance, has_internal_guidance, has_internal_guidance_section, has_external_guidance, has_publisher_guidance)) %>%
  pivot_longer(cols = !journal, names_to = 'topic', values_to = 'value') %>%
  group_by(journal) %>%
  summarise(topics_mentioned = sum(value)) %>%
  arrange(topics_mentioned) %>%
  pull(journal)

>>>>

# list of journals in order of most topics mentioned
journals_topics_mentioned_ordered <- d_internal_guidance %>%
  # Recode NAs to FALSE
  mutate(across(
    starts_with('has_'), ~replace_na(., FALSE) )) %>% 
  mutate(journal = toupper(journal)) %>%
  select(journal, starts_with("has_"), -c(has_guidance, has_internal_guidance, has_internal_guidance_section, has_external_guidance, has_publisher_guidance)) %>%
  pivot_longer(cols = !journal, names_to = 'topic', values_to = 'value') %>%
  group_by(journal) %>%
  summarise(topics_mentioned = sum(value)) %>%
  arrange(topics_mentioned) %>%
  pull(journal)
